### 2014-03-05 src/paper.Rnw
update

% 10 pages for the main text + 1 for references.
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
<<test, child='intro.Rnw'>>=
@
<<test, child='related.Rnw'>>=
@
<<test, child='methodology.Rnw'>>=
@
<<test, child='analysis.Rnw'>>=
@

@@

\section{Results}

>>>>

% 10 pages for the main text + 1 for references.
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@

@@

<<results, child='results.Rnw'>>=
@

\begin{enumerate}
\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
\item [TODO] We should check if the distribution significantly different too.
\item [DONE] Use sampling
\item [DONE] Check on randoop samples too
\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
\item [DONE] Compare random selection with class, method, and mutagen sampling.
\item [TODO] Report time for each, as cost.
\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
\end{enumerate}
\section{Results}
